Efficient Machine Learning in a Memristor Network

### 2025-04-07 paper/paper.tex
First sketch of plot regression is ready

Recent advances in AI systems have been powered by the silicon-based computing power of the Graphics Processing Units (GPUs) and by an unprecedented abundance of data. With a clear trend of larger ANN models, their the energy requirements have grown significantly, negatively impacting their efficiency and scalability\cite{energy_cost_ml1, energy_cost_ml2}. 
These networks typically operate in two phases: inference and backpropagation.

% ## Physical Neural Networks ##
% - what they are, what is the scope (physical instead of math training)
% - advantages: faster, computations are less energy demanding.

While the inference energy consumption has been addressed by hardware accelerators, the backpropagation still remains a problem. As an alternative to ANN performed strictly in-silico, physical neural networks (PNN) have been introduced, where physical processes rather than mathematical operations are trained\cite{}. In fact, physical processes are often faster and consume less energy than their digital counterpart.

% ## PNN algorithms in literature ##

>>>>

Recent advances in AI systems have been powered by the silicon-based computing power of the Graphics Processing Units (GPUs) and by an unprecedented abundance of data. With a clear trend of larger ANN models, their the energy requirements have grown significantly, negatively impacting their efficiency and scalability\cite{energy_cost_ml1, energy_cost_ml2}. With the rapid increase in computation requirements of AI training and the slower improvemnts in computing hardware traditionally predicted by Moore's Law, the necessity of new computing paradigms became more relevant.  As an alternative to ANN performed strictly in-silico, physical neural networks (PNN) have been introduced, where physical processes rather than mathematical operations are trained\cite{trainingphysicalneuralnetworks}. Since physical processes can be faster and more energetically efficient than their digital representation, this direction constitutes a promosing research direction to address this issue.
